Static Analysis by Path Focusing

### 2011-06-13 report/report.tex
bug fix in the report

\usetikzlibrary{snakes,arrows,shapes,backgrounds,shadows,automata,patterns}
\usepgflibrary{snakes}

@@

\subsubsection{Sources of imprecision}
 \label{multigraph}
Linear Relation Analysis is sound but incomplete: there is loss of precision
during the computation, due to various reasons:
\begin{enumerate}
\item Since an abstract domain is used to represent the set of possible states,
such as the domain of convex polyhedra, there is an upper approximation of the
set of possible states to the smallest convex polyhedron including this set. This
loss of precision is unavoidable. Still, there are techniques proposing to
compute disjunctive invariants \cite{GulwaniZ10} to limit this upper approximation: at each
program point, a union of convex polyhedra is computed instead of a single
one.
\item The widening operator, used to ensure convergence of the technique,
also induces a loss of precision. The classical technique is then to compute
narrowing iterations, which often recover some precision.

@@

	As explained in \ref{multigraph}, separating the different
	possible paths between $p$ and $q$ reduce the number of points with a join
	operation, and results in a better precision.
	This can result in an exponential blowup in the size of the graph. To avoid
	it, the technique is to never construct the multigraph, and only compute
	parts of it when needed.

>>>>

\usetikzlibrary{snakes,arrows,shapes,backgrounds,shadows,automata,patterns}
%\usepgflibrary{snakes}

@@

\subsubsection{Sources of imprecision}
 \label{imprecision}
Linear Relation Analysis is sound but incomplete: there is loss of precision
during the computation, due to various reasons:
\begin{enumerate}
\item Since an abstract domain is used to represent the set of possible states,
such as the domain of convex polyhedra, there is an upper approximation of the
set of possible states to the smallest convex polyhedron including this set. This
loss of precision is unavoidable. Still, there are techniques proposing to
compute disjunctive invariants \cite{GulwaniZ10} to limit this upper approximation: at each
program point, a union of convex polyhedra is computed instead of a single
one.
\item The widening operator, used to ensure convergence of the technique,
also induces a loss of precision. The classical technique is then to compute
narrowing iterations, which often recover some precision.

@@

	As explained in \ref{imprecision}, separating the different
	possible paths between $p$ and $q$ reduce the number of points with a join
	operation, and results in a better precision.
	This can result in an exponential blowup in the size of the graph. To avoid
	it, the technique is to never construct the multigraph, and only compute
	parts of it when needed.
